\begin{flushleft}
\hangindent=2em
\hangafter=1
[1] Bakshi and Madan. (2000), “Spanning and Derivative-Security Valuation,” \emph{Journal of Financial Economics}, 55, Vol. 2, 205–238.

\hangindent=2em
\hangafter=1
[2] Barndorff-Nielsen. (1997), “Processes of Normal Inverse Gaussian Type,” \emph{Finance and Stochastics}, 2, Vol. 1, 41–68.

\hangindent=2em
\hangafter=1
[3] Bates. (1996), “Jumps and Stochastic Volatility: Exchange Rate Processes Implicit in Deutsche Mark Options,” \emph{Review of Financial Studies}, 9, Vol. 1, 69–107. 

\hangindent=2em
\hangafter=1
[4] Carr and Madan. (1999), “Option Valuation Using the Fast Fourier Transform,” \emph{The Journal of Computational Finance}, 2, Vol. 4, 61–73.

\hangindent=2em
\hangafter=1
[5] Duffie, Pan, and Singleton. (2000), “Transform Analysis and Asset Pricing for Affine Jump-Diffusions,” \emph{Econometrica}, 68, Vol. 6, 1343–1376. 

\hangindent=2em
\hangafter=1
[6] Fang, and Oosterlee. (2009), “A Novel Pricing Method for European Options Based on Fourier-Cosine Series Expansions,” \emph{SIAM Journal on Scientific Computing }, 31, Vol. 2, 826–48.

\hangindent=2em
\hangafter=1
[7] Guo, Hung, and So. (2009), “A Generalization of the Barone-Adesi and Whaley Approach for the Analytic Approximation of American Options,” \emph{Journal of Futures Markets}, 29, Vol. 5, 478–493.

\hangindent=2em
\hangafter=1
[8] Heston. (1993), “A Closed-Form Solution for Options with Stochastic Volatility with Applications to Bond and Currency Options,” \emph{The Review of Financial Studies }, 6, Vol. 2, 327–343.

\hangindent=2em
\hangafter=1
[9] Kou. (2002), “A Jump-Diffusion Model for Option Pricing,” \emph{Management Science}, 48, Vol. 8, 1086-1101.

\hangindent=2em
\hangafter=1
[10] Lewis. (2001), “A Simple Option Formula for General Jump-Diffusion and Other Exponential Levy Processes,” \emph{SSRN Electronic Journal}. 

\hangindent=2em
\hangafter=1
[11] Macovschi and Quittard-Pinon. (2006), “On the Pricing of Power and Other Polynomial Options,” \emph{The Journal of Derivatives}, 13, Vol. 4, 61–71.

\hangindent=2em
\hangafter=1
[12] Madan, Carr, and Chang. (1998), “The Variance Gamma Process and Option Pricing,” \emph{Review of Finance}, 2, Vol. 1, 79–105.

\hangindent=2em
\hangafter=1
[13] Makate and Sattayatham. (2011), “Stochastic Volatility Jump-Diffusion Model for Option Pricing,” \emph{Journal of Mathematical Finance}, 1, Vol. 3, 90–97.

\hangindent=2em
\hangafter=1
[14] Merton. (1976), “Option Pricing When Underlying Stock Returns Are Discontinuous,” \emph{Journal of Financial Economics}, 3, Vol. 1–2, 125–144.

\hangindent=2em
\hangafter=1
[15] Wang J.Y., Wang C.J., Dai, Chen, Liu, and Zhou. (2022), “Efficient and Robust Combinatorial Option Pricing Algorithms on the Trinomial Lattice for Polynomial and Barrier Options,” \emph{Mathematical Problems in Engineering}, Vol. 2022.
\end{flushleft}